---
title: "ChatGPT examples and responses"
date: "`r Sys.Date()`"
format: html
execute: 
  eval: false
---

# Question 1

Write me some R code using the mtcars dataset to plot a comparison of miles per gallon versus car model

## Answer

```{r}
# Load the mtcars dataset (it should already be available in R)
data(mtcars)

# Plotting the comparison of miles per gallon (mpg) versus car model
plot(mpg ~ as.factor(row.names(mtcars)), data = mtcars, 
     xlab = "Car Model", ylab = "Miles per Gallon", 
     main = "Comparison of Miles per Gallon by Car Model",
     col = "blue", pch = 16, cex = 1.5)
```

# Question 2

Make me an R shiny app with the following dataset to plot a time series of sd_m versus SampleTime with options to select by epchc_station

$ bay_segment            <chr> …
$ epchc_station          <dbl> …
$ SampleTime             <dttm> …
$ yr                     <dbl> …
$ mo                     <dbl> …
$ Latitude               <dbl> …
$ Longitude              <dbl> …
$ Total_Depth_m          <dbl> …
$ Sample_Depth_m         <dbl> …
$ tn                     <dbl> …
$ tn_q                   <chr> …
$ sd_m                   <dbl> …
$ sd_raw_m               <dbl> …
$ sd_q                   <chr> …
$ chla                   <dbl> …
$ chla_q                 <chr> …
$ Sal_Top_ppth           <dbl> …
$ Sal_Mid_ppth           <dbl> …
$ Sal_Bottom_ppth        <dbl> …
$ Temp_Water_Top_degC    <dbl> …
$ Temp_Water_Mid_degC    <dbl> …
$ Temp_Water_Bottom_degC <dbl> …
$ `Turbidity_JTU-NTU`    <chr> …
$ Turbidity_Q            <chr> …
$ Color_345_F45_PCU      <chr> …
$ Color_345_F45_Q        <chr> …

## Answer

```{r}
library(shiny)
library(ggplot2)

# Replace 'your_data.csv' with the path to your dataset file
dataset <- read.csv("your_data.csv")

ui <- fluidPage(
  titlePanel("Time Series Plot of sd_m vs SampleTime"),
  sidebarLayout(
    sidebarPanel(
      selectInput("station", "Select Station:", choices = unique(dataset$epchc_station)),
      dateRangeInput("dateRange", "Select Date Range:",
                     start = min(dataset$SampleTime), end = max(dataset$SampleTime))
    ),
    mainPanel(
      plotOutput("timeSeriesPlot")
    )
  )
)

server <- function(input, output) {
  filteredData <- reactive({
    dataset %>%
      filter(epchc_station == input$station,
             SampleTime >= input$dateRange[1] & SampleTime <= input$dateRange[2])
  })
  
  output$timeSeriesPlot <- renderPlot({
    ggplot(filteredData(), aes(SampleTime, sd_m)) +
      geom_line() +
      labs(x = "Sample Time", y = "sd_m") +
      theme_minimal()
  })
}

shinyApp(ui, server)
```

# Question 3

Convert this SAS code to R:

/* Step 1: Import the dataset */
/* Replace 'your_dataset.csv' with the path to your dataset file */
/* If the dataset is in the same folder as your SAS program, you can use a simple filename */
data work.your_data;
   infile 'your_dataset.csv' delimiter=',' dsd firstobs=2;
   input
      bay_segment : $50.
      epchc_station
      SampleTime : datetime.
      yr
      mo
      Latitude
      Longitude
      Total_Depth_m
      Sample_Depth_m
      tn
      tn_q : $10.
      sd_m
      sd_raw_m
      sd_q : $10.
      chla
      chla_q : $10.
      Sal_Top_ppth
      Sal_Mid_ppth
      Sal_Bottom_ppth
      Temp_Water_Top_degC
      Temp_Water_Mid_degC
      Temp_Water_Bottom_degC
      Turbidity_JTU_NTU : $10.
      Turbidity_Q : $10.
      Color_345_F45_PCU : $10.
      Color_345_F45_Q : $10.
   ;
   format SampleTime datetime20.;
run;

/* Step 2: Select specific columns */
/* Here, we select the columns 'SampleTime' and 'sd_m' */
data work.selected_data;
   set work.your_data (keep=SampleTime sd_m);
run;

/* Step 3: Filter rows based on a condition */
/* Here, we filter rows where 'sd_m' is greater than 0 */
data work.filtered_data;
   set work.selected_data;
   where sd_m > 0;
run;

/* Step 4: Create a scatter plot of two variables */
/* Here, we plot 'sd_m' against 'SampleTime' */
/* Replace 'png' with other formats like 'gif', 'jpeg', or 'pdf' for the output file */
ods graphics on;
proc sgplot data=work.filtered_data;
   scatter x=SampleTime y=sd_m;
   xaxis label="Sample Time";
   yaxis label="sd_m";
run;
ods graphics off;

## Answer

```{r}
library(dplyr)
library(ggplot2)

# Step 1: Import the dataset
# Replace 'your_dataset.csv' with the path to your dataset file
# Use read.csv() to read the CSV file
your_data <- read.csv('your_dataset.csv', header = TRUE)

# Step 2: Select specific columns
# Here, we select the columns 'SampleTime' and 'sd_m'
selected_data <- your_data %>%
  select(SampleTime, sd_m)

# Step 3: Filter rows based on a condition
# Here, we filter rows where 'sd_m' is greater than 0
filtered_data <- selected_data %>%
  filter(sd_m > 0)

# Step 4: Create a scatter plot of two variables
# Here, we plot 'sd_m' against 'SampleTime'
# Replace 'png' with other formats like 'png', 'jpeg', or 'pdf' for the output file
png('scatter_plot.png')
ggplot(filtered_data, aes(x = SampleTime, y = sd_m)) +
  geom_point() +
  xlab("Sample Time") +
  ylab("sd_m")
dev.off()
```