---
title: "Piney Point Data and Analysis"
author: "[Dr. Marcus Beck](mailto:mbeck@tbep.org) $\\bullet$ [\\@fawda123](https://twitter.com/fawda123)	$\\bullet$ [#TampaBayOpensci](https://twitter.com/hashtag/TampaBayOpenSci?src=hashtag_click)"
institute: "Tampa Bay Estuary Program"
date: "6/15/2021"
output:
  xaringan::moon_reader:
    nature:
      highlightLines: true
      countIncrementalSlides: false
      ratio: '16:9'
    lib_dir: libs
    css: styles.css
    includes: 
      after_body: insert-logo-tbep.html
---

```{r, message = F, echo = F, warning = F}
library(knitr)
library(tidyverse)
library(lubridate)
library(extrafont)
library(xaringanExtra)
library(sf)

use_panelset()

source(file = "https://raw.githubusercontent.com/EvaMaeRey/little_flipbooks_library/master/xaringan_reveal_parenthetical.R")

loadfonts(device = 'win', quiet = T)

fml <- 'Lato Light'

# global knitr options
opts_chunk$set(message = FALSE, dev.args = list(family = fml), dpi = 300, dev = 'png', echo = F, warning = F, fig.align = 'center', out.width = '100%')
```

class: left, top

.center[
# Goals for today
]

* Understand the available data
* Understand how to access the available data
* Analyses to date
* Develop analysis goals and plan of attack
* Meeting notes [here](https://docs.google.com/document/d/1gWFnNe5kPj5rLmgmrLbVlt2UsxfE4pX1v6Gfdh8HbZc/edit)

---

class: left, top

.center[
# Data in hand
]

* All raw data from partners are here (spreadsheet, GoogleDrive): https://bit.ly/3wtC5gz
* All compiled/formatted data are here (.RData, GitHub): https://github.com/tbep-tech/piney-point/tree/main/data)

---

class: left, top

.center[
# Data in hand
]

* __Water quality__: 17 parameters
* __Phytoplankton__: qualitative, quantitative
* __Seagrass, macroalgae__: Freq. occurrence by species, groups
* __Contaminants__: mostly metals
* __Baseline__: water quality and seagrass
* __Spatial__: monitoring stations by type 

---

class: left, top

.center[
# Data in hand
]

* All data pulled from GoogleDrive and synthesized using [this](https://github.com/tbep-tech/piney-point/blob/main/R/dat_proc.R) R script 
     * Compile by source (e.g., DEP, Manatee Co., etc.)
     * Standardize names, units, etc.
     * Organize in tidy format for ease of analysis
* Each time data are updated, several automated [tests](https://github.com/tbep-tech/piney-point/tree/main/tests/testthat) are run to check accuracy, e.g., 
     * Are the units, names correct?
     * Are the station names matching between files?
     * Are their duplicates, missing values?

---

class: left, top

.center[
# Getting the data
]

* All files are in .RData binary formats, access in R (I can make csv if needed)
* Files follow a loose naming convention, e.g.,
   * `rswqdat`: response water quality data
   * `bswqdat`: baseline water quality data
   * `rstrndat`: response SAV, macroalgae transect data
   * `rsphydat`: response phytoplankton data
   * `rstrnpts`: response transect spatial data (points)
   
---

class: left, top

.center[
# Getting the data
]

* All files are "tidy" and able to join by station, source and/or date

```{r, echo = T}
load(url('https://tbep-tech.github.io/piney-point/data/rswqdat.RData'))
rswqdat
```

---

class: left, top

.center[
# Analyses to date
]

* Some preliminary stuff: [https://github.com/tbep-tech/piney-point-analysis](https://github.com/tbep-tech/piney-point-analysis)
     * [Interpolation example](https://tbep-tech.github.io/piney-point-analysis/chlinterp): chlorophyll response
     * [Trends synthesis](https://tbep-tech.github.io/piney-point-analysis/trends): poor attempt at broad analysis
     * [Seasonal analysis](https://tbep-tech.github.io/piney-point-analysis/seasonal): deviation from baseline relative to hydrology
* The data folder in this repo is synced daily with the source data on the Piney Point dashboard repo
* Open for GitHub Pull Requests

---

class: left, top

.center[
# Analysis goals
]

* We know there was an initial water column algal response
* We need to show other responses, the nutrients did not go away: 
     * Nutrient recycling between parts of the bay
     * Broad vs local changes
     * Deviation from baseline
     * Link to modelling data
* Immediate concern is documenting impacts, but long-term plan is publication
